---
title: "Pretty Simulation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("GeneOverlap")
library("gdata")
library("VennDiagram")
library("gplots")
library("ggplot2")

library("grid")
library("gridExtra")
library("lattice")



```


```{r, inclue = FALSE}
theme<-theme(panel.background = element_blank(),
             panel.border=element_rect(fill=NA),
             panel.grid.major = element_line(colour="grey90", size=0.5),
             panel.grid.minor = element_blank(),
             strip.background=element_blank(),
             axis.title = element_text(colour="black", face="bold"),
             axis.text=element_text(colour="black"),
             axis.ticks=element_line(colour="black"),
             plot.margin=unit(c(1,1,1,1),"line"),
             plot.title = element_text(hjust = 0.5))
```

# Simulation

The following simulation calculates the size of overlap between two randomly generate lists from a base of **20,210**, the number of protein encoding genes in the mouse genome (see below). 

A list of **5000** 'genes' (in this case random integers) will randomly be picked from an integer list of 1 to 20,210.

**100000** trials will be run.

```{r}
# set.seed?

gs_mouse = 20210
samplesize = 5000
trials = 100000

IntersectionCounts <- sapply(1:trials,
                 function(IntersectCount)
                   c(IntersectCount,length(intersect(sample(gs_mouse, samplesize), sample(gs_mouse, samplesize)))))

# format IntersectionCounts
IntersectionCounts <- as.data.frame(t(IntersectionCounts))
colnames(IntersectionCounts) <- c("Trial","Intersections")
head(IntersectionCounts)
```

```{r histogram simulation}
histo <- ggplot(IntersectionCounts, aes(x=Intersections))+
  geom_histogram(alpha = .5, color = "black", fill = "#7B409A")+
  xlab("Number of Overlapping Genes")+
  ylab("Count")+
  geom_vline(aes(xintercept=mean(IntersectionCounts$Intersections)),
            color="#7B409A", linetype="dashed", size=1, show.legend=TRUE)+
  theme(panel.background = element_blank(),
             panel.border=element_rect(fill=NA),
             panel.grid.major = element_line(colour="grey90", size=0.5),
             panel.grid.minor = element_blank(),
             strip.background=element_blank(),
             axis.title = element_text(colour="black", face="bold"),
             axis.text=element_text(colour="black"),
             axis.ticks=element_line(colour="black"),
             plot.margin=unit(c(1,1,1,1),"line"),
             plot.title = element_text(hjust = 0.5))
histo
```
```{r}
tiff(filename = "Histo_sim.tiff", width = 6, height = 4, units = "in", res = 300)
histo
dev.off()
```





```{r}
histod <- ggplot(IntersectionCounts, aes(x=Intersections))+
  geom_histogram(aes(y = ..density..),alpha = .5, color = "black", fill = "#7B409A")+
  geom_density(fill=NA, color = "black") +
  theme(panel.background = element_blank(),
             panel.border=element_rect(fill=NA),
             panel.grid.major = element_line(colour="grey90", size=0.5),
             panel.grid.minor = element_blank(),
             strip.background=element_blank(),
             axis.title = element_text(colour="black", face="bold"),
             axis.text=element_text(colour="black"),
             axis.ticks=element_line(colour="black"),
             plot.margin=unit(c(1,1,1,1),"line"),
             plot.title = element_text(hjust = 0.5))
histod
```






The mean intersection size is **`r mean(IntersectionCounts[,"Intersections"])`**. 

```{r venn_simulation, include=FALSE}

# randomList <- replicate(15, sample(gs_mouse, samplesize))

venns <- lapply(1:10, function(i)
  grobTree(draw.pairwise.venn(5000, 5000, IntersectionCounts[i, "Intersections"],
           fill=c("darkmagenta", "darkblue"),
           alpha=c(0.5,0.5),
           cex = 0.5,
           main= paste("Venn", i), main.cex = 2)))

# gs <- lapply(1:9, function(ii) 
#   grobTree(rectGrob(gp=gpar(fill=ii, alpha=0.5)), textGrob(ii)))
# grid.arrange(grobs=gs, ncol=4, 
#                top="top label", bottom="bottom\nlabel", 
#                left="left label", right="right label")
# grid.rect(gp=gpar(fill=NA))
# see: https://cran.r-project.org/web/packages/gridExtra/vignettes/arrangeGrob.html

```









```{r, echo=FALSE, fig.height=2.1, fig.width=5, fig.align='center'}

title=textGrob("Example Random Overlaps", gp=gpar(fontface="bold", fontfamily="Times"))

# tiff(filename = "Venn_simulation.tiff", width = 10, height = 4.3, units = "in", res = 300)

grid.arrange(grobs=venns, ncol=5,
             top=title)
# dev.off()
```